Using traffic analysis to identify The Second Generation Onion Router

### 2010-12-18 thesis/experiment.tex
Quick description of setting up selenium

>>>>

\subsubsubsection{Selenium}

SSL + Tor over selenium.

Generate a selenium firefox profile. First launch selenium in interactive mode specifying a proxy:

java -jar $selenium.jar -interactive

This will start a prompt to which you can edit commands, you must launch a browser to get selenium to create a firefox profile directory.

cmd=getNewBrowserSession&1=*firefoxproxy&2=http://www.google.com

Generate a firefox profile, then edit the proxy.pac file to

function FindProxyForURL(url, host) {
   if(shExpMatch(url, '*/selenium-server/*')) {
       return 'PROXY localhost:4444; PROXY proxy.ourdomain.dom:8080';
   } else if (shExpMatch(host, '*dev.ourdomain.dom*')) {
       return 'DIRECT';
   } else if (shExpMatch(host, '*qa.ourdomain.dom*')) {
       return 'DIRECT';
   } else if (shExpMatch(host, '*staging.ourdomain.dom*')) {
       return 'DIRECT';
   } else {
       return 'PROXY proxy.ourdomain.dom:8080';
   }
}

or

function FindProxyForURL(url, host) {
   if(shExpMatch(host, '*torsim')) {
       return 'PROXY localhost:8118';
   }
   return 'PROXY localhost:4444; DIRECT';
}

This makes sure that your proxy (Tor) gets used for outgoing connections, and the selenium proxy is used for running tests.

To get SSL certificates accepted, you must manually accept them permanently for each host. This will update the cert_override.txt and cert8.db files.

Tor must have the following setting supplied:

ExitPolicyRejectPrivate 0

Since we are using a 192.* network. - Not true, testing mode flag sets this.

But the tor relays must be able to resolve names using DNS, if you use socks4a protocol.
